\documentclass[10pt,a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1.7cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{setspace}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=4.5mm, topsep=1pt, itemsep=1pt, parsep=0pt}
\setstretch{1.0}

\newcommand{\sectionline}[1]{
\vspace{4pt}
\begin{center}
\textbf{\large #1}
\end{center}
\vspace{-1.5mm}
\hrule
\vspace{3pt}
}

\newcommand{\expentry}[4]{
\textbf{#1} \hfill \textbf{#2}\\
#3 \hfill #4
}

\newcommand{\eduentry}[4]{
#1 \hfill \textbf{#2}\\
#3 \hfill #4
}

\begin{document}

\begin{center}
\begin{tikzpicture}
\end{tikzpicture}

{\LARGE\textbf{CRISTIAN HERIBERTO TASCÓN MUÑOZ}}\\
Backend Developer | Full Stack Developer | Innovation \& Development Analyst\\
cristiantmm11@outlook.com \; \textbullet \;linkedin.com/in/cristiantasconm \; \textbullet Github.com/cristianT2002 \textbullet \; Bogot\'a, D.C., Colombia 
\end{center}

\sectionline{Professional profile}

Electronics engineer with more than 3 years of experience building backend software solutions for industrial and technology environments, including projects for major companies in oil \& gas and telecommunications. I specialize in software architecture design, computer vision system integration, and automation, with strong Python, Flask, FastAPI, JavaScript, and SQL skills, and full-stack ability to design and integrate complete web platforms with React and Tailwind CSS.

\sectionline{Experience}

\expentry{Axure Technologies}{Colombia}{Frontend Developer}{01/2026 -- Present}
\begin{itemize}
    \item Redesigned an industrial monitoring web platform in React, implementing an interactive map with Leaflet.js and a real-time dashboard, improving visualization and traceability of operational and historical data.
    \item Optimized rendering and component architecture in key modules, reducing interface response times by 30\%.
\end{itemize}

\expentry{Freelancer}{Colombia}{Full Stack Developer}{10/2025 -- 03/2026}
\begin{itemize}
    \item 
Designed and implemented a relational PostgreSQL database for an operational activity management and tracking platform in telecommunications, built with React and Flask, optimizing the schema for efficient queries over large data volumes.
    \item 
Automated bulk data loads and repetitive tasks, reducing manual effort for the operations team by 40\% and information registration time.
    \item Identified and resolved bottlenecks across frontend, backend, and database, improving overall system stability and performance.

\end{itemize}

\expentry{Axure Technologies}{Colombia}{Innovation \& Development Analyst / Backend Developer}{06/2023 -- 03/2026}
\begin{itemize}
    \item Led refactoring of the backend for a real-time security equipment monitoring system using computer vision, implementing YOLO models and dataset training for oil \& gas clients such as Ecopetrol, significantly improving system stability and maintainability.
    \item Implemented Clean Architecture and an event bus--driven design with production optimizations that cut RAM usage by 50\%.
    \item Strengthened software quality and security with unit tests, testing strategies, and solid versioning practices on GitHub and GitLab.
    \item Managed production environments with Docker and integrated monitoring with Grafana and Prometheus to track key system metrics and shorten detection and response times for production incidents.
    \item Designed a predictive analytics solution with machine learning and PRTG API integration to estimate depletion dates for consumption in telecommunications infrastructure, reducing extra-consumption costs by 98\%.
\end{itemize}

\expentry{Axure Technologies}{Colombia}{Electronics Engineering Intern}{12/2022 -- 06/2023}
\begin{itemize}
    \item Implemented an environmental monitoring system with electrical measurement sensors for racks with solar power generation.
    \item Built Python modules for focus stacking in a mineral categorization and visualization system.
\end{itemize}

\sectionline{Education}
\eduentry{Universidad de San Buenaventura}{Bogot\'a, Colombia}{B.S. Electronics Engineering}{2024}

\sectionline{Technical skills}
Python, TypeScript, JavaScript, SQL, C/C++, HTML, CSS, Flask, REST APIs, React, Tailwind CSS, Bootstrap, Docker, Git, GitHub, GitLab, Linux, CI/CD, Postman, Grafana, Prometheus, YOLO, Raspberry Pi, ESP32.

\sectionline{Certifications}
\textbf{Python Data Architect (Basic -- Intermediate)} \dotfill \ Bootcamp Institute\\
\textbf{Introduction to Modern AI} \dotfill \ Cisco Networking Academy

\sectionline{Soft skills}
\textbf{Self-directed learner}\\
I acquire new knowledge and tools on my own, adapting to each project's technical demands.

\textbf{Adaptability}\\
I adjust easily to changes in role, technology, or context while keeping the team's goals in focus.

\textbf{Teamwork}\\
I collaborate actively with different profiles, contributing to an aligned, results-oriented work environment.

\textbf{Assertive communication}\\
I express ideas, progress, and risks clearly and respectfully, supporting decision-making in technical and business teams.

\textbf{Resilience}\\
Under obstacles or high-pressure environments, I stay calm, analyze the situation, and get back on track quickly.


\end{document}
